### 2021-03-06 article/paper_eng.tex
fixed geometry
fixed plot

% \listfiles
\documentclass[a4paper,10pt]{article}
\usepackage[T2A]{fontenc}
% \usepackage[english, russian]{babel}
\usepackage{sectsty}
\sectionfont{\centering\normalfont}
\subsectionfont{\centering\normalfont}
\subsubsectionfont{\normalfont}
\usepackage{changepage}
\usepackage{filecontents}
\usepackage{array}
\usepackage{float} 
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage[14pt]{extsizes}
\usepackage{physics} 
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{../misc/}}
\usepackage{setspace,amsmath}
\usepackage{bigstrut}
\usepackage{tabularx}
% \usepackage[left=30mm, right=15mm, top=20mm, bottom=20mm]{geometry} 
\usepackage[nottoc]{tocbibind}
\usepackage[style=gost-numeric,sorting=none,backend=biber,defernumbers=false]{biblatex}
\DeclareBibliographyAlias{misc}{article}
\addbibresource{lit.bib} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \everymath{\displaystyle}
% \DeclareMathSizes{12}{20}{14}{10}

@@

\begin{figure}
\centering
\begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio=true]{weights_XY_good_ru.pdf}
    \caption{Highly specialized neurons, compeition weights equal --100}
    \label{fig:high_comp}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio=true]{weights_XY_bad_ru.pdf}
    \caption{Poorly specialized neurons, compeition weights equal --10}
    \label{fig:low_comp}
\end{subfigure}
\caption{The effect of competition on $ XY $ connections training.}
\label{competition-training-importance}
\end{figure}

>>>>

% \listfiles
\documentclass[a4paper,10pt]{article}
\usepackage[T2A]{fontenc}
% \usepackage[english, russian]{babel}
\usepackage{sectsty}
% \sectionfont{\centering\normalfont}
% \subsectionfont{\centering\normalfont}
% \subsubsectionfont{\normalfont}
\usepackage{changepage}
\usepackage{filecontents}
\usepackage{array}
\usepackage{float} 
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage[14pt]{extsizes}
\usepackage{physics} 
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{../misc/}}
\usepackage{setspace,amsmath}
\usepackage{bigstrut}
\usepackage{tabularx}
\usepackage[left=15mm, right=15mm, top=15mm, bottom=15mm]{geometry} 
\usepackage[nottoc]{tocbibind}
\usepackage[style=gost-numeric,sorting=none,backend=biber,defernumbers=false]{biblatex}
\usepackage{multicol}
\DeclareBibliographyAlias{misc}{article}
\addbibresource{lit.bib} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \everymath{\displaystyle}
% \DeclareMathSizes{12}{20}{14}{10}

@@

\begin{figure}
\centering
\begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio=true]{weights_XY_good.pdf}
    \caption{Highly specialized neurons, compeition weights equal --100}
    \label{fig:high_comp}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth,keepaspectratio=true]{weights_XY_bad.pdf} 
    \caption{Poorly specialized neurons, compeition weights equal --10}
    \label{fig:low_comp}
\end{subfigure}
\caption{The effect of competition on $ XY $ connections training.}
\label{competition-training-importance}
\end{figure}
